Verifying Demonstrations

### 2020-07-02 paper/intro.tex

Our last contribution is another version of the protocol, one which uses 
bit-by-bit transmissions as traditionally done with \ac{DB} protocols.
We achieve all properties except \ac{DBTF} resistance.

The first (and second) contribution enables us to do distance-bounding 
privacy-preserving attribute-based credentials based on discrete logarithms, 
\eg \cite{Camenisch-phdthesis} and \cite{CLsignatures}.
To our knowledge, no other distance-bounding protocol achieves this.
The third contribution (bit-by-bit version) also enables us to do the same, 
just without \ac{DBTF} resistance.

@@

The paper is organized as follows.
\Cref{related-work} discusses related work.
\Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
\Cref{DB-Schnorr} introduces the first version, where we assume that we can 
send all bits at the same time.
\Cref{DB-Schnorr-PKI} introduces the \ac{PKI} and \ac{AKE} to use the first 
version of the protocol in practice.
\Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
\Cref{formal-verification} describes our effort to formally verify the protocol 
using Tamarin.
Finally, we conclude with discussion and conclusions in 
\cref{Discussion,Conclusion}.

>>>>

Our last contribution is another version of the protocol, one which uses 
bit-by-bit transmissions as traditionally done with \ac{DB} protocols.
We achieve all properties except \ac{DBTF} resistance.
We see this contribution as merely for the sake of completion, as the previous 
contributions are slightly more efficient.

The first (and second) contribution enables us to do distance-bounding 
privacy-preserving attribute-based credentials based on discrete logarithms, 
\eg \cite{Camenisch-phdthesis} and \cite{CLsignatures}.
We can do this by simply replacing their use of the Schnorr 
protocol~\cite{Schnorr} for \acp{ZKPK} with our protocol in this paper.
To our knowledge, no other distance-bounding protocol achieves this.
The third contribution (bit-by-bit version) also enables us to do the same, 
just without (full) \ac{DBTF} resistance.

@@

The paper is organized as follows.
\Cref{related-work} discusses some related work.
\Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
\Cref{DB-Schnorr} introduces the first version, where we assume that we can 
send all bits at the same time.
\Cref{DB-Schnorr-PKI} introduces the \ac{PKI} and \ac{AKE} to use the first 
version of the protocol in practice.
\Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
\Cref{formal-verification} describes our effort to formally verify the protocol 
using Tamarin.
Finally, we conclude with discussion and conclusions in 
\cref{Discussion,Conclusion}.
